\section*{Appendix}
\section{Deployment to Real Bitcoin}
\import{./}{algorithms/alg.bitcoin-real.tex}

The algorithm works as follows. Initially, the user generates a fresh dust key
$(pk, sk)$ to which they will receive their newly generated tokens. \todo{TODO:
What do these keys look like?} From the $pk$, the user derives a $64$-byte
\emph{key reference} $pkr = \textsf{SHA512}(pk)$. The key reference is then
treated as an uncompressed Bitcoin or Bitcoin Cash public key pair, i.e., its
first $32$-byte part is considered the $X$ coordinate and the second $32$-byte
part is considered the $Y$ coordinate of an elliptic curve. The key reference is
then prefixed with \texttt{0x04} and the result is hashed using
$\textsf{RIPEMD160}(\textsf{SHA256}(\cdot))$ as is usual for address generation.
This produces the \emph{key hash reference} $pkh$. The least significant bit of
$pkh$ is then flipped. This step is imperative to the security of the scheme to
ensure that the generated address is unspendable. This produces the $20$-byte
\emph{perturbated key hash reference} $pkh'$. The perturbated key hash reference
is then prefixed with \texttt{0x00} for the Bitcoin mainnet or with
\texttt{0x6f} for the Bitcoin testnet as usual. The checksum of the prefixed
perturbated key hash reference is then calculated as the last $4$ bytes of
$\textsf{SHA256}(\textsf{SHA256}(prefix || pkh'))$. These $4$ bytes are appended
to the prefixed perturbated key hash reference as a suffix, and the result is
\textsf{base58} encoded into a bitcoin address.

\import{./}{algorithms/alg.construction-real.tex}

\section{Computational Indistinguishability}

\import{.}{./algorithms/alg.dist-game.tex}

We review the definition of computational indistinguishability between two
distributions $X$ and $Y$. Define the cryptographic game illustrated in
Algorithm~\ref{alg.dist-game}.
Computational indistinguishability mandates that no adversary can win the game,
except with negligible probability.

\begin{definition}[Computational indistinguishability]
  Two distribution ensembles $\{X_\kappa\}_{\kappa\in\mathbb{N}}$ and $\{Y_\kappa\}_{\kappa\in\mathbb{N}}$ are
  \emph{computationally indistinguishable}
  if for every probabilistic polynomial-time adversary $\mathcal{A}$,
  there exists a negligible function $negl$ such that
  $\Pr[\textsc{dist-game}_{\mathcal{A},X,Y}(\kappa) = \true] < negl(\kappa)$.
\end{definition}
