\section{Empirical Results}

\newcommand{\rref}[1]{}

In order to evaluate our consumption mechanisms, we implement the federated consumption mechanism in Solidity. We provide a concrete implementation of the \textsf{burn-verifier} contract described in Algorithm~\rref{alg.burn-verifier} as \textsf{BurnedBTC}. We implement the \textsf{Crosschain} parent contract from~\cite{pow-sidechains}. In order to achieve this we implement our own verification methods similar to \rref{alg.verify-event-federation} in our \textsf{Verifier} library. Specifically, we verify transaction data in \textsf{Verifier} similarly to \rref{alg.verify-tx} by making use of the open source bitcoin-spv library~\cite{bitcoin-spv-library}. We verify block connection using a Merkle Mountain Range where each leaf corresponds to a block. The leaf stores the Merkle Tree root of the Merkle Tree which collects the transaction id of the transactions included in the block in question.

We put forth the \textsf{BurnVerifier} library which provides a concrete implementation for our berning protocol. Specifically the library implements the \textsf{BurnVerify} function of the protocol. Finally, the federation voting happens in the \textsf{CheckpointRepo} contract, which is initialized with the addresses belonging to the federation members. The members can then proceed to call the \textsf{CheckpointRepo.vote} method to vote on their MMR computed from the source blockchain.

We release our implementation as open source software under the MIT license.
\footnote{
    \ifanonymous
        The link to our open source software implementation, which uses the MIT license, has been redacted for anonymity.
    \else
        \url{https://github.com/decrypto-org/burn-paper/tree/master/experiment}.
    \fi
}
The implementation is production-ready and fully tested with 100\% code coverage.

Using prices at the time of writing, we obtain a median gas price of $6.9$ gwei and the price of $1$ ETH = $\$170.07$, giving a gas price of $\$1.173483 * 10^{-6}$.

\begin{center}
    \begin{tabular}{ |c|c|c| }
     \hline
     Method & Gas cost & Equivalent in USD \\
     \hline
     \textsf{CheckpointRepo.vote} & 43039 gas & $\$0.05$ \\
     \textsf{BurnedBTC.claim} & 232926 gas & $\$0.27$ \\
     \hline
    \end{tabular}
\end{center}

For the end user to claim his burn, the cost is thus \$0.27. Comparatively, for a Bitcoin transaction to be included in the next block at the time of writing a user would have to spend \$0.77.
